%!TEX TS-program = xelatex
\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[scale=0.93]{geometry}

% moderncv themes
\moderncvstyle{banking} 
\moderncvcolor{blue} 

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.94]{geometry}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,    % Set to true to enable links without colors
    linkcolor=black,    % Set link color to black
    filecolor=black,    
    urlcolor=black,
}

% personal data
\name{Vincent}{Chen}
\email{zhong\_chen233@gmail.com}
\social[linkedin]{zihong-chen}
\social[github]{zihongchen}

\begin{document}
\makecvtitle

\section{Experience}


\cventry{Jul 2022 -- Present}{Software Engineer, Android \& AI}{Google Photos}{Mountain View, CA}{}{
    \begin{itemize}
        \item Developed "Ask Photos," a multimodal AI agent enabling users to search photos by chatting \underline{\href{https://techcrunch.com/2024/05/14/google-photos-introduces-an-ai-search-feature-ask-photos/}{(TechCrunch)}}.
            \begin{itemize}
                \item Built responsive, ChatGPT-like streaming interface using Kotlin,  Coroutines, Jetpack Compose, Dagger/Hilt, MVVM. 
                \item Overhauled Android client's search, delivering relevance-based results using multimodal embeddings, replacing timestamp sorting.
                \item Collaborated with DeepMind to optimize agent performance through prompt engineering, fine-tuning, and model evaluation.
            \end{itemize}
        \item Led development of "Photo Stack," which groups similar photos and reduces gallery clutter by 33\% for 1B+ users \underline{\href{https://techcrunch.com/2023/11/15/google-photos-turns-to-ai-to-organize-and-categorize-your-photos-for-you/}{(TechCrunch)}}.
            \begin{itemize}
                \item Designed data models for Photo Stack and implemented core features, including sharing, favoriting, deleting, and unstacking.
                \item Minimized main gallery jank with SQL query optimization, paging, lazy loading, caching, performance profiling. 
            \end{itemize}
        \item Completely rewrote Google Photos settings from Java to Kotlin and Material Design 3, decluttering the settings by 50\%.
         \underline{\href{https://www.phonearena.com/news/google-photos-redesigned-settings-menu_id147974}{(Article)}}. 
    \end{itemize}}

\cventry{Sep 2023 -- Apr 2024}{Tech Lead \& AI Engineer}{PeerTalent}{San Francisco, CA}{}{
    \begin{itemize}
        \item Led team of 7 to build AI platform analyzing peer reviews/video interviews for job candidate ranking.
        \item Designed backend APIs, modified Elo rating algorithms, and utilized LLMs for resume evaluation.
    \end{itemize}}

\cventry{Jan 2023 -- Jun 2023}{Co-Founder \& CTO}{StarAI}{San Francisco, CA}{}{
    \begin{itemize}
        \item Founded startup creating autonomous celebrity AI chatbots using OpenAI, LangChain, Pinecone, Text-to-speech(TTS), Telegram.
        \item Partnered with a Forbes 30 under 30 winner and a 5M+ follower celebrity, growing community to 1,000+ members in 2 months.
        \item Led team of FAANG engineers to build asynchronous platform (Asyncio, Flask) handling 500K concurrent users with 99\% uptime.
\end{itemize}}

\cventry{May 2021 -- Aug 2021}{Data Engineer Intern}{Amazon}{Jersey City, NJ}{}{
    \begin{itemize}
         \item Developed real-time dashboards by unifying 6 microservices, achieving \$800k+ annual savings and 7x faster access to critical metrics. 
        \item Designed and built ETL data pipelines with CDK, Glue, Spark, S3 to load 22B+ records daily into Redshift to power dashboards.
        \item Redesigned Redshift schema, reducing size by over 50\% across 56 tables, and implemented pipeline tests to ensure data integrity.
    \end{itemize}}

\cventry{Mar 2020 -- Jun 2020}{Co-Founder \& Back-end Engineer}{Tar Heel Mask Initiative LLC}{Chapel Hill, NC}{}{
    \begin{itemize}
        \item Founded an e-commerce platform, grossing \$100K in revenue in 2 months and leading a cross-functional team of 7. 
        \item Developed backend (Python, BeautifulSoup) to scrape 40K local business contacts and automate email marketing campaign.
    \end{itemize}}

\cventry{Jan 2020 -- Jul 2020}{NLP Research Intern}{Acta Solutions LLC}{Chapel Hill, NC}{}{
    \begin{itemize}
        \item Engineered BERT-based transformer models with PyTorch to summarize and analyze sentiments of 100K+ government surveys.
        \item Reached ROUGE-1 score of 40 on extractive summarization on CNN/Daily Mail, competitive with then-current SOTA models.
    \end{itemize}}

\section{Projects}

\cventry{}{Distributed Training and Fine-tuning of a Custom Transformer Model (Outperformed GPT-3 on HellaSwag)}{}{}{}{
    \begin{itemize}
        \item Designed and trained a 124M parameter decoder-only transformer from scratch. 
        \item Utilized the FineWeb dataset and distributed training (DDP, 8 NVIDIA H100 GPUs) to accelerate training.
    \end{itemize}}

\section{Skills}
\cvitem{AI/ML}{LLMs, RAG, Agents, PyTorch, Prompt Engineering, Fine-tuning, RLHF, LangChain, Pinecone}
\cvitem{Android/Backend}{AndroidX, Java, Kotlin, Jetpack Compose, MVVM, Coroutine, Python, Nodejs, Flask, Django}
\cvitem{Data \& Infrastructure}{SQL, MongoDB, MySQL, Docker, Kubernetes, Azure, AWS, CI/CD}

\section{Education}

\cventry{May 2022}{B.S. Computer Science; B.S. Business Administration}{University of North Carolina at Chapel Hill}{}{}{}

\end{document}